\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-13 jss/article.tex
removing sd.shrinkage

\subsection{Rao-Blackwellized Coverage Probability}
Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were fixed at first (see 5.1) and $z_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates (numeric values) on the $i$-th dataset. We can calculated this probability exactly because we know the distribution of $(p_{ij} \vert z_{ij}, r, \beta)$ in (9). Then, we can estimate the first player's coverage probability, for instance, by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
\section[Example]{Example}
\subsection[Known Prior Mean]{Known Prior Mean}
Using 10 hospital data with PR
\subsection[Unknown Prior Mean and No Covariate]{Unknown Prior Mean and No Covariate}
Using 8 school data with GR
\subsection[Unknown Prior Mean and One Covariate]{Unknown Prior Mean and One Covariate}
Using 18 baseball data with BR

>>>>

\subsection{Rao-Blackwellized Coverage Probability}
Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were fixed at first (see 5.1) and $z_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates (numeric values) on the $i$-th dataset. We can calculated this probability exactly because we know the distribution of $(p_{ij} \vert z_{ij}, r, \beta)$ in (9). Then, we can estimate the first player's coverage probability, for instance, by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$.
\section[Example]{Example}
\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
If you, living in the New York state (NY), were suffering from severe coronary heart disease (hopefully not), and were supposed to receive the coronary artery bypass graft (CABG) surgery, your concern might be each hospital's abililty to handle this surgery.
\\

For this purpose, you gathered data of 31 hospitals in NY composed of the number of deaths within a month of CABG surgeries and total number of patients receiving CABG surgeries in each hospital. In addition, suppose you could obtaion the state-level death rate of this surgery while you were looking for such information, which was 0.02. From this point, there are a lot of ways to explore those data to have an idea about each hospital's ability. 
\\

One way we suggest here is a hierarchical modeling assuming that there is a bigger population-level hierarchy. In this case, for example, we presume that there is a state-level (NY) hierarchy governing the true death rates of CABG surgery of all the hospitals in NY. Then, we can consider the true death rates of those 31 hospitals were sampled from this state-level population distribution whose mean is 0.02. The validity of such an assumption can be checked (Christiansen and Morris, 1996).
\\

Once we are sure that the assumption of an additional hierarchy is reasonable, we start a model-fitting process.  Since the true death rate after CABG surgery might be small and caseloads ($n_{j}$) look relatively much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data. Next, \code{gbp} will help us fit a multi-level model with the Gamma conjugate distribution for $\lambda_{j}$ on the second-level hierarchy whose mean is 0.02 ($\lambda_{0}=0.02$) as described in the section 3.2.
\begin{CodeChunk}
\begin{CodeInput}
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for whole observations:

           sample.mean        n prior.mean shrinkage sd.shrinkage post.intv.low post.mean post.intv.upp post.sd
1                0.045   67.000       0.02     0.834        0.056         0.011     0.024         0.042   0.008
2                0.029   68.000       0.02     0.832        0.057         0.010     0.022         0.038   0.007
3                0.024  210.000       0.02     0.616        0.095         0.011     0.021         0.035   0.006
4                0.043  256.000       0.02     0.568        0.099         0.017     0.030         0.046   0.008
5                0.033  269.000       0.02     0.556        0.099         0.015     0.026         0.041   0.007
6                0.044  274.000       0.02     0.551        0.100         0.018     0.031         0.047   0.008
7                0.043  278.000       0.02     0.548        0.100         0.018     0.030         0.047   0.007
8                0.014  295.000       0.02     0.533        0.100         0.008     0.017         0.029   0.005
9                0.029  347.000       0.02     0.492        0.101         0.014     0.024         0.038   0.006
10               0.037  349.000       0.02     0.491        0.101         0.017     0.029         0.043   0.007
11               0.039  358.000       0.02     0.484        0.101         0.018     0.030         0.045   0.007
12               0.018  396.000       0.02     0.459        0.100         0.010     0.019         0.030   0.005
13               0.028  431.000       0.02     0.438        0.099         0.015     0.024         0.037   0.006
14               0.025  441.000       0.02     0.433        0.099         0.013     0.023         0.035   0.005
15               0.027  477.000       0.02     0.414        0.098         0.015     0.024         0.036   0.006
16               0.045  484.000       0.02     0.410        0.098         0.023     0.035         0.050   0.007
17               0.030  494.000       0.02     0.405        0.097         0.016     0.026         0.039   0.006
18               0.022  501.000       0.02     0.402        0.097         0.012     0.021         0.032   0.005
19               0.028  505.000       0.02     0.400        0.097         0.015     0.025         0.036   0.005
20               0.020  540.000       0.02     0.384        0.095         0.012     0.020         0.031   0.005
21               0.028  563.000       0.02     0.374        0.094         0.016     0.025         0.037   0.005
22               0.024  593.000       0.02     0.362        0.093         0.014     0.022         0.033   0.005
23               0.015  602.000       0.02     0.358        0.093         0.010     0.017         0.026   0.004
24               0.024  629.000       0.02     0.348        0.092         0.014     0.023         0.033   0.005
25               0.020  636.000       0.02     0.346        0.091         0.012     0.020         0.030   0.005
26               0.048  729.000       0.02     0.316        0.087         0.027     0.039         0.053   0.007
27               0.031  849.000       0.02     0.284        0.082         0.019     0.028         0.038   0.005
28               0.027  914.000       0.02     0.269        0.080         0.017     0.025         0.035   0.005
29               0.021  940.000       0.02     0.264        0.079         0.014     0.021         0.030   0.004
30               0.029 1193.000       0.02     0.220        0.070         0.020     0.027         0.036   0.004
31               0.020 1340.000       0.02     0.201        0.065         0.014     0.020         0.027   0.003
== Mean ==       0.029  517.032       0.02     0.438        0.091         0.015     0.025         0.037   0.006
\end{CodeOutput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{hospital1.png}
\caption{Shrinkage and interval plots of 31 hospitals in NY}
\end{center}
\end{figure}

\subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{school1.png}
\caption{Shrinkage and interval plots of 8 schools}
\end{center}
\end{figure}

\subsection[Unknown Second-level Mean and One Covariate]{18 Baseball Players: Unknown Prior Mean and One Covariate}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{baseball1.png}
\caption{Shrinkage and interval plots of 18 baseball players}
\end{center}
\end{figure}
